IML Term project paper

### 2022-12-23 paper.rmd
Update paper.rmd
Tarkemmat arvot taulukossa Lassolle, logistiselle regressiolle ja SVM:lle

The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.87 & 1.36&0.84\\
Naive Bayes & 0.81 & 152.85&\\
LDA & 0.89 & 1.33&\\
QDA & 0.85 & 6.34&\\
SVM & 0.88 & -&0.84\\
Lasso & 0.89 & 1.29&0.87\\
Random Forest & 0.89 & 1.35&\\
\hline
\end{tabular}
\end{table}

@@

```{r}
summary(npfOrig)
```

>>>>

The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.8728448 & 1.338286\\
Naive Bayes & 0.81 & 152.85\\
LDA & 0.89 & 1.33\\
QDA & 0.85 & 6.34\\
SVM & 0.8793103 & -\\
Lasso & 0.8965517 & 1.29399\\
Random Forest & 0.89 & 1.35\\
\hline
\end{tabular}
\end{table}

@@

```{r}
summary(npfOrig)
```
\newpage
# References
